---
title: "Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#loading in the dataset

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)
```

#Problem 1

```{r}
class(choco)
rate <- choco$Rating
hist(rate)
```
# From the above, we can see that there are some outliers between 1-2 and there are no ratings which are above 5 either

```{r}
boxplot(rate)
```
# From the boxplot, we are able to draw the same conclusions as the histrogram. We can see that there are 4 outlier points and there are no ratings above 5 in the scale

# Problem 2
```{r}
unique(choco$Location)
numRate <- table(choco$Location)
numRate2 <- sort(numRate, decreasing = TRUE)
numRate2
```
# Most ratings are from the USA by over 5 times the second most. The second largest bunch is from France, Canada and U.K.
```{r}
barplot(numRate2)
```
# As we can see from the above graph, most of the ratings are from USA. There is a large difference between the first and second country with regards to the ratings. The countries which follow USA with ratings are France, Canada and UK


#Problem 3
```{r}
perc <- choco$Cocoa_Percent
plot(perc,rate)
```
#Not that good, data all over the place
```{r}
cor(perc,rate)
```
#Low correlation value
```{r}
summary(perc)
summary(rate)
best <- rate[rate == 4]
length(best)
choco1 <- order(choco$Rating, decreasing = TRUE)
fours <- choco1[1:102]
bestcho <- choco[fours,]
bestperc <- bestcho$Cocoa_Percent
hist(bestperc)
summary(bestperc)
```
#The best chocolate has around 70 Cocoa Percent

#Problem 4
```{r}
unique(choco$Bean_Origin)
origin <- choco$Bean_Origin
oritab <- table(choco$Bean_Origin)
most <- sort(oritab, decreasing = TRUE)
most
Vene <- choco[origin == 'Venezuela', ]
unique(Vene$Characteristics1)
unique(Vene$Characteristics2)
Peru <- choco[origin == 'Peru', ]
unique(Peru$Characteristics1)
unique(Peru$Characteristics2)
Vietnam <- choco[origin == 'Vietnam', ]
unique(Vietnam$Characteristics1)
```
  
# I am using characteristics 1-4 to represent the flavors of the chooclate
# There is a large variety of flavors from the two countries that produce chocolate, so it is safe to assume that a specific flavor does not come from a specific place
# I also tested a random country in the middle and there was a large variety of flavors from there too

```{r}
bestori <- table(bestcho$Bean_Origin)
bestori1 <- sort(bestori, decreasing = TRUE)
plot(bestori1, xlab = 'countries', ylab = 'number of 4 rates')
```

# It does not look like there is a best origin as the highest ranking of chocolates come from multiple countries
# The highest amounts were Venezuela and Peru, but they produced the most chocolate as well
# Comparing it to the highest amount of origins, it loosely follows the countries that produce to most chocolate
# Some countries that produce a lot did not produce any 4 rate chocolate (Dominican Republic), so origin does has some effect

#Problem 5
#(First Analysis - Rithwik Gokhale)
# My analysis will be comparing the years of the chocolate manufacturing vs the % cacao in the chocolates being compared.

```{r}
years <- choco$Date
unique(sort(years, decreasing = TRUE))
```

```{r}
cor(choco$Date, choco$Cocoa_Percent)
plot(choco$Date, choco$Cocoa_Percent)
```
#As we can see from the above graphs, there is very little positive correlation between the two variables of manufacturing year and the %cacao in the chocolates. Furthermore, from the graph, we can also see that the % of cacao was going up from 2006 to the yeat 2014 but then started to decrease afterwards. This suggests that having less % of cacao in the chocolate became a trend from the year 2014. This analysis can be used to determine how the % of cacao in the chocolate influences the ratings of the chocolate over the years. 

#(Second Analysis - Tyren Teav)

